---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

This is mostly an experimental project in building a package and understanding ggplot themes better, but if it turns out to be helpful and you have suggestions I am definitely interested in hearing from you. Hit me up on [twitter](https://twitter.com/wytham88). 

## Install
```{r, eval = FALSE}
devtools::install_github("weiyangtham/econothemes")
```

### NBER theme

ggplot2 theme inspired by the NBER's [Reporter](http://www.nber.org/reporter/) and [Digest](http://www.nber.org/digest/). 

The relevant functions are `theme_nber()`, `scale_color_nber()`, and `scale_fill_nber()`. 

Note that the scales draw on a palette with only two colors. The NBER typically uses a sequential palette of different shades of blue, which doesn't work so well with more than two values. If you want to stay true to that style, you can try building a sequential palette with [ColorBrewer](http://colorbrewer2.org/#type=sequential&scheme=Blues&n=3) or using the [RColorBrewer](https://cran.rstudio.com/web/packages/RColorBrewer/RColorBrewer.pdf) package. 

#### Example
```{r, message = FALSE, warning = FALSE}
library(gapminder)
library(tidyverse)
library(econothemes)

df = filter(gapminder, country %in% c("United States", "United Kingdom"))

ggplot(df, aes(year, lifeExp, color = country)) + 
  geom_line() + 
  theme_nber() + 
  scale_colour_nber() + 
  labs(title = "Life Expectancy in US and UK", 
       subtitle = "theme_nber() example", 
       caption = "Source: Gapminder")

```

